The pollination trade-off

### 2018-11-14 paper/manuscript.Rmd
Intro to second objective

## Data collection

We performed sampling in three locations, each located in a distinct region of the Argentinian Pampas. 
The sampling locations are distributed across a gradient of precipitation with a humid temperate climate in the eastward Flooding Pampas and an drier as we move inland and westward towards the Pampean Grasslands.
Across all sites, annual mean temperatures range between 14.8 and 15.8 Celsius.

>>>>

## Effect of ecological factors in the pollination service

Our second objetive is to investigate the relative contribution that different factors that describe the plants' role and its ecological context have on the pollination service. 
Specifically, we investigate the effect of (*i*) the number of shared pollinators, (*ii*) the plants relative abundance, (*iii*) the plants functional originality, and (*iv*) the mean visit effectiveness---a metric that combines the share of pollen that a plant species is able to place on each of their floral visitors and the number of visits it receives from them. 
Here, we define visit efectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*.
